### 2014-06-03 ACL2014/experiments.tex
updating experiment section

\subsection{Data}
The first data set is the one made avialble to the public from the AOL search engine \cite{Pass06} (denoted as \aol dataset). 
In addition, a large query log 
from a commercial search engine, denoted as Qlogs, is used for evaluations.
As Qlogs typically reaches to hundres of millions of queries over multiple days (i.e., $N=600$ million unique queries\footnote{this does not represent an exhaustive set of queries posed to the search engine.}.) We then generated multiple datasets from Qlogs by sampling at various size rates. \dataA represents a $1\%$ sample from Qlogs, \dataB represents a $10\%$ sample and \dataC represents the entire Qlogs. 
For each query $q$, a feature vector in a high dimensional feature space is defined as
$\qvec = (f_1, f_2, \cdots, f_D)$, where $f_i$ is a click through rate of url $i$ and query $q$.
%For each query $q$, a high dimensional and sparse feature vector was created over clicked urls (the number of usrls is a few billion). Specifically, each dimension in the feature vector of $q$ corresponds to a weight of a webpage (urls) that have received a user click for $q$. The weight of an url for $q$ is defined as the click through rate of the url.  
Note that in a pre-processing step, we remove all the queries that have less than or equal to five clicked urls. 
Table \ref{tab:data} summarizes the statistics of our query-log datasets.

@@

In the first experiment, we vary the similarity threshold parameter $\tau$ to be in $\{0.7,0.8,0.9\}$ 
while fixing $K=16$ and $L=10$ for the \aol and \dataA datasets. 
From Table~\ref{tab:varyTau}, $\tau=0.9$ achieves higher recall than that of $\tau=0.7$.
This is expected as finding near duplicates is easier than finding near neighbors. For, rest of this paper, 
we fix $\tau=0.7$ as we are interested in both near-duplicates and nearest-neighbors for our test queries.

>>>>

\subsection{Data}
The first data set is the one made avialble to the public from the AOL search engine \cite{Pass06} (denoted as \aol dataset). 
In addition, a large query log 
from a commercial search engine, denoted as Qlogs, is used for evaluations.
As Qlogs typically reaches to hundres of millions of queries over multiple days (i.e., $N=600$ million unique queries\footnote{this does not represent an exhaustive set of queries posed to the search engine.}.) We then generated multiple datasets from Qlogs by sampling at various size rates. \dataA represents a $1\%$ sample from Qlogs, \dataB represents a $10\%$ sample and \dataC represents the entire Qlogs. 
For each query $q$, a feature vector in a high dimensional feature space is defined as
$\qvec = (f_1, f_2, \cdots, f_D)$, where $f_i$ is a click through rate of url $i$ and query $q$. Note that in our real implementation, $\qvec$ follows a spare representaion omitting dimensions with zero click through rate.
%For each query $q$, a high dimensional and sparse feature vector was created over clicked urls (the number of usrls is a few billion). Specifically, each dimension in the feature vector of $q$ corresponds to a weight of a webpage (urls) that have received a user click for $q$. The weight of an url for $q$ is defined as the click through rate of the url.  
Note that in a pre-processing step, we remove all the queries that have less than or equal to five clicked urls. 
Table \ref{tab:data} summarizes the statistics of our query-log datasets.

@@

In the first experiment, we vary the similarity threshold parameter $\tau$ to be in $\{0.7,0.8,0.9\}$ 
while fixing $K=16$ and $L=10$ for the \aol and \dataA datasets. 
Table~\ref{tab:varyTau} shows that $\tau=0.9$ achieves higher recall than that of $\tau=0.7$.
This is expected as finding near duplicates is easier than finding near neighbors. For, rest of this paper, 
we fix $\tau=0.7$ as we are interested in both near-duplicates and nearest-neighbors for our test queries.
